Future Directions

### 2021-04-04 manuscripts/laplacian_smoothing/arXiv/appendix.tex
few more changes mostly to Appendix + questions

\citet{calder2019} take $\Xset$ to be a smooth submanifold of $\Rd$ without boundary, i.e. they assume $\Xset$ satisfies~\ref{asmp:domain_manifold}. In this setting, they exhibit an absolutely continuous measure $\wt{P}_n$ with density $\wt{p}_n$ that with high probability is close to $P_n$ in transportation distance, and for which $\|p - \wt{p}_n\|_{\Leb^\infty}$ is also small. In Proposition~\ref{prop:optimal_transport}, we adapt this result to the setting of full-dimensional manifolds with boundary.  
\begin{proposition}
	\label{prop:optimal_transport}
	Suppose $\Xset$ satisfies~\ref{asmp:domain} and $p$ satisfies~\ref{asmp:density}. Then with probability at least $1 - A_0 n \exp\bigl\{-a_0 n\theta^2\wt{\delta}^d\bigr\}$, the following statement holds: there exists a probability measure $\wt{P}_n$ with density $\wt{p}_n$ such that:
	\begin{equation}
	\label{eqn:optimal_transport_1}
	d_{\infty}(\wt{P}_n, P_n) \leq A_0 \wt{\delta}
	\end{equation}
	and
	\begin{equation}
	\label{eqn:optimal_transport_2}
	\|\wt{p}_n - p\|_{\infty} \leq A_0\bigl(\wt{\delta} + \theta\bigr)
	\end{equation}
\end{proposition}
For the rest of this section, we let $\wt{P}_n$ be a probability measure with density $\wt{p}_n$, that satisfies the conclusions of Proposition~\ref{prop:optimal_transport}. Additionally we denote by $\wt{T}_n$ an \emph{optimal transport map} between $\wt{P}_n$ and $P_n$, meaning a transportation map which achieves the infimum in \eqref{eqn:optimal_transport}. Finally, we write $U_1,\ldots,U_n$ for the preimages of $X_1,\ldots,X_n$ under $\wt{T}_n$, meaning $U_i = \wt{T}_n^{-1}(X_i)$.

@@

\textit{Case 1: $d < 2$.}
The $\Leb^4(\Xset)$-norm of $f$ can be bounded in terms of the $\Leb^2(\Xset)$ norm,
\begin{align*}
\norm{f}_{\Leb^4(\Xset)}^4 & \leq \left(\sup_{x \in \Xset} \abs{f(x)}\right)^2 \cdot \int_{\Xset} [f(x)]^2 \,dx \leq C_7^2 M^2 \cdot \|f\|_{\Leb^2(X)}^2.
\end{align*}
Since by assumption
\begin{equation*}
\norm{f}_{\Leb^2(\Xset)}^2 \geq C_6^2 \cdot b^2 \cdot M^2 \cdot \frac{1}{n},
\end{equation*}
we have
\begin{equation*}
p_{\max} \frac{\norm{f}_{\Leb^4(\Xset)}^4}{n} \leq C_7^2 M^2p_{\max} \cdot \frac{\norm{f}_{\Leb^2(\Xset)}^2}{n} \leq \frac{C_7p_{\max}}{C_6^2 b^2} \norm{f}_{\Leb^2(\Xset)}^4 \leq \frac{\Ebb\bigl[\norm{f}_n^2\bigr]}{b^2},
\end{equation*}
where the last inequality follows by taking $C_6 \geq C_7 \sqrt{p_{\max}/p_{\min}}$.

@@

\paragraph{Bounds on $\Leb^2(\Xset)$ error under Lipschitz assumption.}
Let $V_1,\ldots,V_n$ denote the Voronoi tesselation of $\Xset$ with respect to $X_1,\ldots,X_n$. Extend $\wh{f}$ over $\Xset$ by taking it piecewise constant over the Voronoi cells, i.e.
\begin{equation*}
\wh{f}(x) := \sum_{i = 1}^{n} \wh{f}_i \cdot \1\{x \in V_i\}.
\end{equation*}
Note that we are abusing notation slightly by also using $\wh{f}$ to refer to this extension.

>>>>

\citet{calder2019} take $\Xset$ to be a smooth submanifold of $\Rd$ without boundary, i.e. they assume $\Xset$ satisfies~\ref{asmp:domain_manifold}. In this setting, they exhibit an absolutely continuous measure $\wt{P}_n$ with density $\wt{p}_n$ that with high probability is close to $P_n$ in transportation distance, and for which $\|p - \wt{p}_n\|_{\Leb^\infty}$ is also small. In Proposition~\ref{prop:optimal_transport}, we adapt this result to the setting of full-dimensional manifolds with boundary.  
\begin{proposition}
	\label{prop:optimal_transport}
	Suppose $\Xset$ satisfies~\ref{asmp:domain} and $p$ satisfies~\ref{asmp:density}. Then with probability at least $1 - A_0 n \exp\bigl\{-a_0 n\theta^2\wt{\delta}^d\bigr\}$, the following statement holds: there exists a probability measure $\wt{P}_n$ with density $\wt{p}_n$ such that:
	\begin{equation}
	\label{eqn:optimal_transport_1}
	d_{\infty}(\wt{P}_n, P_n) \leq A_0 \wt{\delta}
	\end{equation}
	and
	\begin{equation}
	\label{eqn:optimal_transport_2}
	\|\wt{p}_n - p\|_{\infty} \leq A_0\bigl(\wt{\delta} + \theta\bigr).
	\end{equation}
\end{proposition}
For the rest of this section, we let $\wt{P}_n$ be a probability measure with density $\wt{p}_n$, that satisfies the conclusions of Proposition~\ref{prop:optimal_transport}. Additionally we denote by $\wt{T}_n$ an \emph{optimal transport map} between $\wt{P}_n$ and $P_n$, meaning a transportation map which achieves the infimum in \eqref{eqn:optimal_transport}. Finally, we write $U_1,\ldots,U_n$ for the preimages of $X_1,\ldots,X_n$ under $\wt{T}_n$, meaning $U_i = \wt{T}_n^{-1}(X_i)$.

@@

\textit{Case 1: $d < 2$.}
The $\Leb^4(\Xset)$-norm of $f$ can be bounded in terms of the $\Leb^2(\Xset)$ norm,
\begin{align*}
\norm{f}_{\Leb^4(\Xset)}^4 & \leq \left(\sup_{x \in \Xset} \abs{f(x)}\right)^2 \cdot \int_{\Xset} [f(x)]^2 \,dx \leq C_7^2 M^2 \cdot \|f\|_{\Leb^2(X)}^2.
\end{align*}
Since by assumption
\begin{equation*}
\norm{f}_{\Leb^2(\Xset)}^2 \geq C_6^2 \cdot b^2 \cdot M^2 \cdot \frac{1}{n},
\end{equation*}
we have
\begin{equation*}
p_{\max} \frac{\norm{f}_{\Leb^4(\Xset)}^4}{n} \leq C_7^2 M^2p_{\max} \cdot \frac{\norm{f}_{\Leb^2(\Xset)}^2}{n} \leq \frac{C_7p_{\max}}{C_6^2 b^2} \norm{f}_{\Leb^2(\Xset)}^4 \leq \frac{\Ebb\bigl[\norm{f}_n^2\bigr]}{b^2},
\end{equation*}
where the last inequality follows by taking $C_6 \geq C_7 \sqrt{p_{\max}/p_{\min}}$. \sbcomment{I'm confused about the last inequality. Are you missing squares on the last term, i.e. $(\Ebb\bigl[\norm{f}_n^2\bigr])^2$ ? I think the problem repeats below but I could be just missing something.}

@@

\paragraph{Bounds on $\Leb^2(\Xset)$ error under Lipschitz assumption.} \sbcomment{This is a nice result but where do you reference it or use it?}
Let $V_1,\ldots,V_n$ denote the Voronoi tesselation of $\Xset$ with respect to $X_1,\ldots,X_n$. Extend $\wh{f}$ over $\Xset$ by taking it piecewise constant over the Voronoi cells, i.e.
\begin{equation*}
\wh{f}(x) := \sum_{i = 1}^{n} \wh{f}_i \cdot \1\{x \in V_i\}.
\end{equation*}
Note that we are abusing notation slightly by also using $\wh{f}$ to refer to this extension.
